---
title: "Three Simulations Assignment"
author: "Cheryl Ngo"
date: "June 9, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1: Wozac
```{r drugs}
oneTimeCost=16
price=3.7
variableCost=.2
operateCost=.4

capacities=seq(30000,60000,5000) #Order quantity

n=10000
maxSimProfs=matrix(ncol=10,nrow=n)

Matrix=matrix(ncol=10,nrow=length(capacities))
for (j in 1:length(capacities)) { 
  for (year in 1:10) {
    yearOneCost=0
    profs=c()
    for (i in 1:n){ #10000 independent replications
      if(year==1) {yearOneCost=oneTimeCost}
      d=rnorm(n=1,mean=50000,sd=12000) #demand
      revenue=min(d,capacities[j])*price
      cost=capacities[j]*(operateCost+yearOneCost)+min(d,capacities[j])*variableCost
      profit=revenue-cost
      profs[i]=profit
    }
    Matrix[j,year]=mean(profs)
    if(j==5) {maxSimProfs[,year]=profs}
  }
}

maximized=50000

expProfit=apply(Matrix,1,sum)
plot(cbind(capacities,expProfit),ylab="Profit",xlab="Capacity",main="Expected Profit by Capacity")
abline(v=maximized,lty=2)
abline(h=expProfit[5],lty=2)

expMaxProfs=apply(maxSimProfs,1,sum)
mean(expMaxProfs)
sd(expMaxProfs)
ci=t.test(expMaxProfs,c(.025,.975))
ci1=ci$conf.int[1]
ci2=ci$conf.int[2]
```

1. I would recommend that they purchase 50,000 units worth of capacity to maximize their profit.  However, if they were looking for a lower upfront cost, they could purchase 45,000 units of capacity to a similar effect.  
2. NuFeel can be 95% certain that mean profit for the 50,000 unit capacity will be between $`r round(ci1)`$ and $`r round(ci2)`$ dollars.  

$$[x-\frac{1.96s}{\sqrt{N}}, x-\frac{1.96s}{\sqrt{N}}]$$

## Question 2: Warranty
```{r warranty}
n=10000
reps=matrix(ncol=3, nrow=n)
for(i in 1:n){
  
  #Sample time until failure
  cost=0
  counter=0
  years=6
  fail=c()
  warranty=0
  while(years>0){
    tToFail=rgamma(n=1,shape=2,scale=.5)
    if(tToFail<1) {
      if(years==6) {cost=100}
      warranty=warranty+1
    }
    if(tToFail>1) {cost=cost+100}
    counter=counter+1
    fail[counter]=tToFail
    years=years-tToFail
  }
reps[i,1]=counter
reps[i,2]=cost
reps[i,3]=warranty
}
par(mfrow=c(3,1))
hist(reps[,2],main="Cost",w=100, xlab="Total Cost");   hist(reps[,3],main="Warranty-Covered  
Failures Purchased in 6-Year Period", xlab="Total Failures");  
hist(reps[,1],main="Devices Owned Within 6 Year-Period", xlab="Total Devices Owned")
mean(reps[,2])
mean(reps[,3])
mean(reps[,1])

```

3. Total cost has an expected value of \$`r mean(reps[,2])`.  I would budget for at least a \$`r ceiling(mean(reps[,2])/100)*100` expense
4. The expected value of the total number of failures during the warranty period is `r mean(reps[,3])`
5. I would expect to own 7 devices since my simulation returned an expected value of `r mean(reps[,1])`

##Question 3: Clearance
```{r clearance}
daysToSell=c()
washerProb=c(.4,.25,.35)
purchProb=.6
arrivals=c(0,1,2,3,4)
probArrival=c(.15,.25,.3,.2,.1)

for(i in 1:10000){
  
  sales=as.data.frame(list(top=5,front=4,frontX=3,washersRemaining=12))
  washers=c("top","front","frontX")
  
  days=1
  
  while(sales[nrow(sales),4]>0){
    
    #Sample number of arrivals
    sampleArrival=sample(size=1,x=arrivals,prob=probArrival,replace=TRUE)
    
    #Sample number of interested
    sampleInterest=sample(size=sampleArrival, x=c(0,1),prob=c(1-purchProb,purchProb), replace=TRUE)
    numInterested=sum(sampleInterest)
    
    #Sample interest type
    sampleType=sample(size=numInterested,x=washers,prob=washerProb,replace=TRUE)
    numTop=sum(sampleType == 'top', na.rm=TRUE)
    numFront=sum(sampleType == 'front', na.rm=TRUE)
    numFrontX=sum(sampleType == 'frontX', na.rm=TRUE)
    
    #Subtract sales from the inventory
    sales[nrow(sales)+1,]=list(ifelse(sales$top[days]-numTop<0,0,sales$top[days]-numTop),  
                               ifelse(sales$front[days]-numFront<0,0,sales$front[days]-numFront), ifelse(sales$frontX[days]-numFrontX<0,0,sales$frontX[days]-numFrontX),0)
    
    sales[nrow(sales),4]=ifelse(sum(sales[days+1,1:3])<0,0,sum(sales[days+1,1:3]))
    
    days= days+1
    
  }
  
  daysToSell[i]=days-1

}

#Histogram of number of days until clearance was sold
hist(daysToSell,main="Days to Sell Clearance Inventory",ylab="Count",xlab="Days",breaks=12)

mean(daysToSell)
qu=quantile(daysToSell,c(.05,.95))
```

It will take on average `r round(mean(daysToSell))` days to sell the clearance merchandise, but they should definitely be prepared for anywhere from `r round(qu[1])` to `r round(qu[2])` days to sell the merchandise.
